---
title: "Exploring Disney movies from 1937 to 2017 gross profits"
output: 
    html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---

**Analysis by: Lilee Yang**


## INTRODUCTION

Disney has been one of the most well known companies in the world with its nostalgic movies. What started as a dream, today it is worth about 168.45 billion ! Lets go back in time and take a look at movies from 1937 to 2016 and their gross profits. 

- Which movies genres have the greatest profits in the years?

- How has Disney movies progressed in popularity?

- What factors play a large role in the rise of Disney?
## Needed packages

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

## Data set

For this analysis I am using a data set created by Dr. Sanchez-Aries. This data set displays the sequence of movies created by Disney with many variables and columns.

```{r}

disney_movies <- read.csv("/cloud/project/data/disneymovie_data.csv" , header = TRUE)
disney_movies
```



## Data Exploration

Before answering our questions about this data set let's explore the possibilities in store. 

In this data set there are a variety of factors that influence the growth of Disney today. From the 578 movies, how many are from each genre?

```{r}
disney_movies %>%
  group_by(genre)%>%
  count() 
```

From these statistics, we can see that Disney made mostly comedy and adventure movies. Some of these movies from the past have become classics most love for a lifetime. 

lets compare the genres and the amount of gross profits they generated.

```{r}

total_gross_by_genre <- disney_movies %>%
  group_by(genre) %>%
  summarise(total_gross_by_genre = sum(total_gross, na.rm = TRUE))

print(total_gross_by_genre)

```




Lets take a look at the top ten movie gross.

```{r}

top_ten_movies <-disney_movies %>%
  arrange(desc(total_gross)) %>%
    slice(1:10)
print(top_ten_movies)

```
how could this differ from the top 10 infliated total gross ?
```{r}

top_ten_inflated_movies <- disney_movies %>%
  arrange(desc(inflation_adjusted_gross)) %>%
  slice(1:10)

print(top_ten_inflated_movies)
```


Next analysis we are going to look at is compairing the years releast and the gross profits

First thing we need to do is break down the data so we only get the year the movie is released.

```{r}
year_release <- disney_movies %>%
  mutate(year_release = year(mdy(release_date)))

year_release
```


```{r}

  ggplot(year_release) +
  geom_point(aes(x = year_release, y =genre, color=MPAA_rating))+
  labs(
    title = "Genres Throughout The Years",
    x = "Year", 
    y = "Genre")

              
```



```{r}

total_gross_by_genre <- disney_movies %>%
  group_by(genre) %>%
summarize(sum(total_gross))

```



```{r}

ggplot(total_gross_by_genre) +
  geom_histogram(aes(x = genre, y = sum(total_gross))) +
  labs(title = "Total Gross by Genre", x = "Genre", y = "Total Gross")

```




```{r}
  ggplot(year_release) +
  geom_point(aes(x =year_release, y =MPAA_rating))+
  labs(
    title = "Audience of Disney",
    x = "Year_released", 
    y = "MPAA Rating")

```

